CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

```{r sex.confounding, fig.width=5, fig.height=4}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
res = lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```

>>>>

```{r sex.confounding, fig.width=5, fig.height=5}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
res = lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```
